Online Learning Your arXiv Preferences

### 2014-05-12 Paper.tex
added basic bar raphs for Precision and Recall.

\noindent Modified Perceptron algorithm:
\begin{quotation}
%\noindent Modified Perceptron:\\
\noindent $w_1=0$\\
{\tt for $t=1$ to $T$}:\\
\indent receive($x_t$)\\
\indent $\widehat{y}_t=\mbox{sign}(w_t\cdot x_t)$\\
\indent {\tt if} $\widehat{y}_t =1$ {\tt or} ($\widehat{y}_t =0$ {\tt and} $k_t = 1$):\\
\indent\indent receive($y_t$)\\
\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
\indent\indent {\tt else $w_{t+1} = w_t$}\\
\indent {\tt else if $\widehat{y}_t = 0$ and $k_t=0$}:\\
\indent\indent $w_{t+1} = w_t$\\
{\tt return $w_{T+1}$}

@@

As mentioned, if the algorithm only made updates when $\widehat{y}=1$ (i.e. interesting) then this would leave the number of mistakes made when $\widehat{y} = 0$ unchecked (and, hence, several lost interesting articles). As a compromise, we generate the i.i.d. variables $k_i$ for each observation when $\widehat{y} = 0$. Note that if $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=0$, the algorithm does not ask for the correct label, and makes no update.

Let $I_1$ be the set of $t$ where a mistake was made and
$\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
$\hat{y} = 0, k = 1$, and let $I_3$ be the set where a mistake was
made, $\hat{y} = 0$ and $k = 0$. Finally, let $M_i = |I_i|$ for $i =
1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
$M$ in the usual perceptron case.  We assume that there exits a $\rho$
and $R$ satisfying the assumptions of Theorem 7.8 from our text, and a separating hyperplane determined by the vector $v$. Let $M' = M_1 + M_2$, then
\begin{align*}
M' =&\ \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2} y_t\V{x}_t \
 \leq   \left\|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t\right\| \\
=& \ \left\|\sum_{t \in I_1 \cup I_2} (\V{w}_{t+1} - \V{w}_t) \right\| 
= \ \|\V{w}_{T+1} \| \\
=&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 - \|\V{w}_t\|^2 }\\
= &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
  \|\V{w}_t\|^2 }\\
= &\ \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
  \|\V{x}_t\|^2} \\
\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
\sqrt{M'r^2} \end{align*}
This implies that $M' \leq \frac{r^2}{\rho^2}$.
We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
Here we revert to a weaker bound, considering the expectation of
$M_3$. Since 
\[M_3 = \sum_{i=1}^m 1_{\left\{\hat{y}_i = 0 \cap y_i = 1\right\}}1_{k_i = 0}, \]
we get that
\begin{align*}
\E[M_3] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 0}] \\
 = &\ (1 - p)\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}],
\end{align*}
where the last equality used the fact that $k_i$ is independent of the data.  Now we want to control the sum of expectations in this expression, and to do this we consider the expectation of $M_2$.
\begin{align*}
M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}1_{k_i = 1} \\
\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\\
\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
\end{align*}
We may then apply the crude bound $\E[M_3] \leq  \frac{1-p}{p}
M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
\begin{align*}
\E[M]  =  &\ \E[M'] + \E[M_3] \\
\leq & \ \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
\leq  & \ \frac{1}{p}\frac{r^2}{\rho^2} \\
\end{align*}
Note that this is a weak bound.  Not only is it greater than the
original perceptron bound by a factor of $\frac{1}{p}$, it is also only a
bound in expectation.

>>>>

\noindent Modified Perceptron algorithm:
\begin{quotation}
%\noindent Modified Perceptron:\\
\noindent $w_1=0$\\
{\tt for $t=1$ to $T$}:\\
\indent receive($x_t$)\\
\indent $\widehat{y}_t=\mbox{sign}(w_t\cdot x_t)$\\
\indent {\tt if} $\widehat{y}_t =1$ {\tt or} ($\widehat{y}_t =-1$ {\tt and} $k_t = 1$):\\
\indent\indent receive($y_t$)\\
\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
\indent\indent {\tt else $w_{t+1} = w_t$}\\
\indent {\tt else if $\widehat{y}_t = -1$ and $k_t=0$}:\\
\indent\indent $w_{t+1} = w_t$\\
{\tt return $w_{T+1}$}

@@

As mentioned, if the algorithm only made updates when $\widehat{y}=1$ (i.e. interesting) then this would leave the number of mistakes made when $\widehat{y} = -1$ unchecked (and, hence, several lost interesting articles). As a compromise, we generate the i.i.d. variables $k_i$ for each observation when $\widehat{y} = 0$. Note that if $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=0$, the algorithm does not ask for the correct label, and makes no update.

Let $I_1$ be the set of $t$ where a mistake was made and
$\hat{y}=1$ (false positives).  Let $I_2$ be the set where a mistake was made and
$\hat{y} = -1, k = 1$ (false negatives where the algorithm updates), and let $I_3$ be the set where a mistake was
made, $\hat{y} = -1$ and $k = 0$ (false negatives where the algorithm does \bold{not} make an update). Finally, let $M_i = |I_i|$ for $i =
1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
$M$ in the usual perceptron case.  We assume that there exits a $\rho$
and $R$ satisfying the assumptions of Theorem 7.8 from our text, and a separating hyperplane determined by the vector $v$. Let $M' = M_1 + M_2$, then
\begin{align*}
M' \rho =&\ \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2} y_t\V{x}_t \
 \leq   \left\|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t\right\| \\
=& \ \left\|\sum_{t \in I_1 \cup I_2} (\V{w}_{t+1} - \V{w}_t) \right\| 
= \ \|\V{w}_{T+1} \| \\
=&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 - \|\V{w}_t\|^2 }\\
= &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
  \|\V{w}_t\|^2 }\\
= &\ \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
  \|\V{x}_t\|^2} \\
\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
\sqrt{M'r^2} \end{align*}
This implies that $M' \leq \frac{r^2}{\rho^2}$.
We then have that $M = M' + M_3$, so we would like a bound on $M_3$, the number of mistakes made that the algorithm does not update on.
Here we revert to a weaker bound, considering the expectation of
$M_3$. Since 
\[M_3 = \sum_{i=1}^m 1_{\left\{\hat{y}_i = 0 \cap y_i = 1\right\}}1_{k_i = 0}, \]
we get that
\begin{align*}
\E[M_3] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 0}] \\
 = &\ (1 - p)\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}],
\end{align*}
where the last equality used the fact that $k_i$ is independent of the data.  Now we want to control the sum of expectations in this expression, and to do this we consider the expectation of $M_2$.
\begin{align*}
M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}1_{k_i = 1} \\
\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}]\\
\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
\end{align*}
We may then apply the crude bound $\E[M_3] \leq  \frac{1-p}{p}
M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
\begin{align*}
\E[M]  =  &\ \E[M'] + \E[M_3] \\
\leq & \ \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
\leq  & \ \frac{1}{p}\frac{r^2}{\rho^2} \\
\end{align*}
Note that this is a weak bound.  Not only is it greater than the
original perceptron bound by a factor of $\frac{1}{p}$, it is also only a
bound in expectation.
